---
title: "GapMinder Analysis"
author: "Tori Osinski"
date: "3/11/2019"
output: 
  html_document: 
    fig_caption: yes
    toc: yes
    keep_md: yes
---
# Introduction

Here is my first RMarkdown document!

# Let's embed some R code

We'll write an R chunk here that loads the tidyverse library and then reads in the GapMinder dataset from our project directory

```{r}
library(tidyverse)
gm <- read_csv("gapminder.csv")
```

# Investigate gm

Let's look at the gm dataset

```{r}
head(gm)
```

#Our first plot

Showing the gdp per capita on the x axis and the life expectancy on the y axis

```{r}
ggplot(gm, aes(gdp_per_cap, lifeexp)) + geom_point()
```

#A better plot

Adding color by continent and adding a log scale for gdp

```{r, fig.cap="Life Expectancy by GDP"}
ggplot(gm, aes(gdp_per_cap, lifeexp)) + 
  scale_x_log10() + 
  geom_point(aes(col = continent))
```

#Option change #1 echo
```{r, fig.cap="Life Expectancy by GDP", echo=FALSE}
ggplot(gm, aes(gdp_per_cap, lifeexp)) + 
  scale_x_log10() + 
  geom_point(aes(col = continent))
```

#Option change #2 fig.show
```{r, fig.cap="Life Expectancy by GDP", fig.show = "hide"}
ggplot(gm, aes(gdp_per_cap, lifeexp)) + 
  scale_x_log10() + 
  geom_point(aes(col = continent))
```

#Option change #3 include
```{r, fig.cap="Life Expectancy by GDP", include = FALSE}
ggplot(gm, aes(gdp_per_cap, lifeexp)) + 
  scale_x_log10() + 
  geom_point(aes(col = continent))
```

# Trying out a kable table

Some data using

```{r}
head(gm)
```

head as a table
```{r}
library(knitr)
kable(head(gm))
```


